Wealth dynamics in the presence of network structure and primitive cooperation

### 2019-07-13 manuscript/verification.tex
Add Figure references; wordsmith.

\begin{figure}[hb]
\centering
\includegraphics[width=\columnwidth]{figures/giniHistory.png}
\caption{The simulated society's wealth inequality over time. (The same
simulation parameters were used as in Figures~\ref{fig:singleRun} and
\ref{fig:effectiveWealthSingleRun}, but this time with 500 agents.)}
\label{fig:giniHistory}
\end{figure}

>>>>

\begin{figure}[hb]
\centering
\includegraphics[width=\columnwidth]{figures/giniHistory.png}
\caption{The simulated society's wealth inequality over time. (The same
simulation parameters were used as in Figures~\ref{fig:singleRun} and
\ref{fig:effectiveWealthSingleRun}, but this time with 500 agents.) The light
blue band represents a bootstrapped 95\% confidence interval.}
\label{fig:giniHistory}
\end{figure}

    The Gini coefficient of the agent population as seen in the top plot of Figure~\ref{fig:giniHistory} is influenced by two distinct dynamics: loss/accumulation of wealth and the formation/death of proto-institutions. Over the course of Stage 1 and the beginning of Stage 3, this change in agent wealth is exclusively responsible for changes in the Gini coefficient. As agents accumulate wealth over Stage 1 and 2, the size of wealth differentials shrinks relative to absolute agent wealth, leading to the declining Gini coefficient. The opposite effect occurs during Stage 3 as agent starvation leads to the relative growth of these wealth differentials. The variability in starvation rates further contributes to the increasing Gini coefficient.

    In addition, as indicated in the bottom plot, the proto formation and proto death also influence the Gini coefficient during Stage 2 and the end of Stage 3, respectively. As expected, the formation of protos during Stage 2 contributes to declining Gini coefficient as the constituent agents of each proto have equivalent wealth values and represent coalitions of perfect economic equality. Accordingly, the death of protos, beginning around Iteration 20, contributes to increase the Gini coefficient by removing the protos' effect on the system's inequality.

    (Note: As the population size decreases over the starvation period, the Gini coefficient becomes increasingly unstable and susceptible to small fluctuations in agent wealth; hence the erratic nature of the red line at the extreme right of Figure~\ref{fig:giniHistory}.)

% vim:textwidth=99999
